A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
Added external dictionaries
Collapsed Figure 5 (number native languages) into the caption on the native language pie chart.

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked turkers to translate individual words, showing each word used in the context of three sentences.  Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.  The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.   The task paid one million dollars for the translation of 10 words.

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\ \hline
No languages&0&1801\\
One language&1&3154\\
Multiple languages&2&243	\\
&3&49\\
&4&12\\
&5&9\\
&6&5\\
&7&2\\
&8&1\\
&9&2\\
&10&2\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-turk-scatter}
\caption{Number of assignments and number of turkers for each language. Each dot represents a language.}
\label{ass-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language. While the bulk (22\%) of bilingual turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent. Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed. As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by turkers located in India.

%%%%%%%%%%%%%%% LOCATION BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-langgeo-sorted}
\caption{Geolocation of turkers speaking 40 most represented languages, in terms of number of assignments submitted}
\label{langgeo-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Self-reported country information is typically reliable. Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses. Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.

>>>>

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.  Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.  The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.   The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
%\begin{figure}[h]
%\begin{tabular}{ccc}\hline\hline
%&\# languages&\# Turkers\\ \hline
%No languages&0&1801\\
%One language&1&3154\\
%Multiple languages&2&243	\\
%&3&49\\
%&4&12\\
%&5&9\\
%&6&5\\
%&7&2\\
%&8&1\\
%&9&2\\
%&10&2\\
%&15&1\\
%\hline\hline
%\end{tabular}
%\label{numlangs-tab}
%\caption{Number of native languages reported during demographic survey.}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-turk-scatter}
\caption{Number of assignments and number of Turkers for each language. Each dot represents a language.}
\label{ass-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language. While the bulk (22\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent. Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed. As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.

%%%%%%%%%%%%%%% LOCATION BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-langgeo-sorted}
\caption{Geolocation of Turkers speaking 40 most represented languages, in terms of number of assignments submitted}
\label{langgeo-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgTurkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Self-reported country information is typically reliable. Three quarters of Turkers who reported their native language reported a single native language consistently across all assignments, and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language.  Less than 5\% of Turkers gave unreasonable responses with 3 or more native languages. Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
